The occurrence rate of long-period exoplanets

### 2016-02-08 document/ms.tex
fancy author latex junk

\documentclass[onecolumn]{aastex6}

@@

\newcommand{\uw}  {Astronomy Department, University of Washington,
                   Seattle, WA, 98195, USA}
\newcommand{\nyu} {Center for Cosmology and Particle Physics,
                   New York University,
                   4 Washington Place, New York, NY, 10003, USA}
\newcommand{\cds} {Center for Data Science, New York University,
                   726 Broadway, 7th Floor, New York, NY, 10003, USA}
\newcommand{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                   K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\newcommand{\mpis}{Max Planck Institute for Intelligent Systems
                   Spemannstrasse 38, 72076 T\"ubingen, Germany}

\author{Daniel~Foreman-Mackey\altaffilmark{1,2}}
\affil{\uw}

\author{David~W.~Hogg}
\affil{\nyu \\ \mpia \\ \cds}

\author{Bernhard~Sch\"olkopf}
\affil{\mpis}

\author{Eric~Agol}
\affil{\uw}

\and

\author{and others}

\altaffiltext{1}{\url{danfm@uw.edu}}
\altaffiltext{2}{Sagan Fellow}

>>>>

\documentclass[preprint]{aastex}

@@

\newcounter{affilcounter}
\setcounter{affilcounter}{2}
\altaffiltext{1}{\url{danfm@uw.edu}; Sagan Fellow}

\edef \uw {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                          Seattle, WA, 98195, USA}

\edef \scda {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\scda}     {Simons Center for Data Analysis, 160 Fifth Avenue,
                          7th floor, New York, NY 10010, USA}

\edef \nyu       {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          New York University,
                          4 Washington Place, New York, NY, 10003, USA}

\edef \cds       {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\cds}      {Center for Data Science, New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}

\edef \mpia      {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\edef \princeton {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}

\edef \mpis      {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    Eric~Agol\altaffilmark{\uw},
    and others
}
